### 2018-04-16 paper.Rmd
minor changes in the comments

The content of CHILDES changes as additional corpora are added or transcriptions are updated; as of the time of writing, these changes are not systematically tracked.
We introduce a simple versioning system by adding a new complete parse of the current state of CHILDES every six months or as warranted by changes in CHILDES.
By default, users interact with the most recent version of the database available. 
But to support reproduction of results with previous versions of the database, we continue to host recent versions (up to the last three years / six versions) through our `childesr` API so that researchers can run analyses against specific historical versions of the database.
For versions more than three years old, we host compressed .sql files that users may download and serve using a local installation of MySQL server.
<!-- SM: How easy is it to implement versioning in the Shiny apps? This would show anyone using the web app the availability of the versions AS: app functionality depends on db version in some cases, so nontrivial -->
<!-- SM: can people get to these sql files currently on the website? AS: yes-->

@@

- Sparsely annotated tiers, e.g. phonology (`%pho`) and situation (`%sit`)
<!--- Media links, including timing information AS: we have media timestamps -->
<!--- Compound word markers, indicated with underscores ("green_eggs_and_ham") AS: we have this -->
- Tone direction and stress
- Filled pauses 
- Reformulations, word revision, and phrase revision, e.g. \textless what did you\textgreater [//] how can you see it ?
- paralinguistic material, e.g. [=! cries]

We will prioritize the addition of these additional information sources in response to community feedback; extending coverage to the above information sources will not require changes to the existing database schema.

@@

We have presented childes-db, a database formatted mirror of the CHILDES dataset.
This database -- together with the `R` API and web apps -- facilitates the use of child language data.
For teachers, students, and casual explorers, the web apps allow browsing and demonstration. For researchers interested in scripting more complex analyses, the API allows them to abstract away from the details of the CHAT format and easily create reproducible analyses of the data.
We hope that these functionalities broaden the set of users who can easily interact with CHILDES data, leading to future insights into the process of language acquisition. 
<!-- need a sentence on how it addresses complex use cases -->

We have created childes-db to address a number of needs in our own teaching and research, but there are still a number of limitations that point the way to future improvements.
For example, currently childes-db operates only on transcript data, without links to the underlying media files; these linkages facilitate deeper analyses of phonology, prosody, social interaction, and many other aspects of acquisition. <!-- SM: I thought we did have media links? -->
Further, we have focused on including the most common and widely-used tiers of CHAT annotation into the database first, but our plan is eventually to include the full range of tiers.
Finally, a wide range of further interactive analyses could easily be added to the current suite of web apps.
We invite other researchers to join us in both suggesting and contributing new functionality as our system grows and adapts to researchers' needs.

>>>>

The content of CHILDES changes as additional corpora are added or transcriptions are updated; as of the time of writing, these changes are not systematically tracked.
We introduce a simple versioning system by adding a new complete parse of the current state of CHILDES every six months or as warranted by changes in CHILDES.
By default, users interact with the most recent version of the database available. 
But to support reproduction of results with previous versions of the database, we continue to host recent versions (up to the last three years / six versions) through our `childesr` API so that researchers can run analyses against specific historical versions of the database.
For versions more than three years old, we host compressed .sql files that users may download and serve using a local installation of MySQL server.
<!-- SM: How easy is it to implement versioning in the Shiny apps? This would show anyone using the web app the availability of the versions AS: app functionality depends on db version in some cases, so nontrivial SM: let's punt-->

@@

- Sparsely annotated tiers, e.g. phonology (`%pho`) and situation (`%sit`)
- Media links
<!--- Compound word markers, indicated with underscores ("green_eggs_and_ham") AS: we have this -->
- Tone direction and stress
- Filled pauses 
- Reformulations, word revision, and phrase revision, e.g. \textless what did you\textgreater [//] how can you see it ?
- paralinguistic material, e.g. [=! cries]

We will prioritize the addition of these information sources in response to community feedback; extending coverage to the above information sources will not require changes to the existing database schema.

@@

We have presented childes-db, a database formatted mirror of the CHILDES dataset.
This database -- together with the `R` API and web apps -- facilitates the use of child language data.
For teachers, students, and casual explorers, the web apps allow browsing and demonstration.
For researchers interested in scripting more complex analyses, the API allows them to abstract away from the details of the CHAT format and easily create reproducible analyses of the data.
We hope that these functionalities broaden the set of users who can easily interact with CHILDES data, leading to future insights into the process of language acquisition.

We have created childes-db to address a number of needs in our own teaching and research, but there are still a number of limitations that point the way to future improvements.
For example, currently childes-db operates only on transcript data, without links to the underlying media files; these linkages facilitate deeper analyses of phonology, prosody, social interaction, and many other aspects of acquisition.
Further, we have focused on including the most common and widely-used tiers of CHAT annotation into the database first, but our plan is eventually to include the full range of tiers.
Finally, a wide range of further interactive analyses could easily be added to the current suite of web apps.
We invite other researchers to join us in both suggesting and contributing new functionality as our system grows and adapts to researchers' needs.
